### 2016-05-10 ch01-intro/introduction.tex
Comments from Anna

\begin{question}[Which non-parametric method should be used for an \gls{FRF}?]
Developing a full parametric model for complicated systems requires considerable effort.
Instead, could we leverage non-parametric or locally parametric approaches to obtain insight in the behavior of the system?
Methods such as the \gls{LPM} and \gls{LRM} can offer good results.
However, it is not clear how these should be tuned for different circumstances (near sharp resonance peaks, in low noise circumstances, \ldots).
Can we devise simple rules that allow one to obtain good \glspl{FRF}?
\end{question}

>>>>

\begin{question}[Which non-parametric method should be used for a \gls{FRF}?]
Developing a full parametric model for complicated systems requires considerable effort.
Instead, could we leverage non-parametric or locally parametric approaches to obtain insight in the behavior of the system?
Methods such as the \gls{LPM} and \gls{LRM} can offer good results.
However, it is not clear how these should be tuned for different circumstances (near sharp resonance peaks, in low noise circumstances, \ldots).
Can we devise simple rules that allow one to obtain good \glspl{FRF}?
\end{question}

### 2016-05-10 ch05-initvals/initial-values.tex
Comments from Anna

In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.

@@

\subsection{System Framework and Model}
\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic \gls{LTI} discrete-time \gls{SISO} system, subjected to a known white random noise input. 
The full model of the system is
\begin{equation}
y(t)=\true{G}(q^{-1})u_0(t)+H_0(q^{-1})e(t)
\label{eq:initial-values:OE:TD}
\end{equation}
where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics, 
$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
We only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{sec:initial-values:ExpMeas}.

@@

With reference to equation \eqref{eq:initial-values:OE:TD}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
\begin{equation}
    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{}  \text{ with }  n \in \IntegerNumbers
\label{ABpolys}
\end{equation}
where $A$ and $B$ are polynomials in $q^{-1}$. 
Thus, it follows from equation \eqref{eq:initial-values:OE:TD} that
\begin{equation}
    \true{G}(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
    \text{.}
\end{equation}

@@

Both systems are low-pass Chebyshev filters which have been generated using the \MATLAB command \mcode[mathescape]{cheby1(2, $\,Q$, 0.05)}.
Their transfer functions are shown in \figref{fig:exampleFRF}.
Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
\begin{equation}
  \mathrm{SNR} 
    = \frac{\sigma_v}
           {\rms{y_0}}
    \approx \frac{\sigma_{v}}
                 {\left\| \true{G} \right\|_2 \rms{u_0}}
    =  \frac{\sigma_{v}}
            {\left\| \true{G} \right\|_2}
  \label{eq:SNR-definition}
  \text{.}
\end{equation}
is attained.
$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.

>>>>

In particular, two different smoothing techniques:
\begin{itemize}
 \item the time-truncated \gls{LPM}~\citep{Lumori2014TIM}, and
 \item the \gls{RFIR}~\citep{Pillonetto2010,Chen2012}
\end{itemize}
are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.

@@

\subsection{System Framework and Model}
\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic \gls{LTI} discrete-time \gls{SISO} system, subjected to a known white random noise input. 
The full model of the system is
\begin{equation}
y(t)=\true{G}(q^{-1})\true{u}(t)+\true{H}(q^{-1})e(t)
\label{eq:initial-values:OE:TD}
\end{equation}
where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $\true{u}(t)$ is the input signal, $v(t)= \true{H}(q^{-1})e(t)$ is the noise source at the output, $\true{H}(q^{-1})$ is the noise dynamics, 
$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
We only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{sec:initial-values:ExpMeas}.

@@

With reference to equation \eqref{eq:initial-values:OE:TD}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
\begin{equation}
    A(q^{-1}) \true{y}(t) = B(q^{-1}) \true{u}(t) \quad \forall t \in n \Ts{}  \text{ with }  n \in \IntegerNumbers
\label{ABpolys}
\end{equation}
where $A$ and $B$ are polynomials in $q^{-1}$. 
Thus, it follows from equation \eqref{eq:initial-values:OE:TD} that
\begin{equation}
    \true{G}(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
    \text{.}
\end{equation}

@@

Both systems are low-pass Chebyshev filters which have been generated using the \MATLAB command \mcode[mathescape]{cheby1(2, $\,Q$, 0.05)}.
Their transfer functions are shown in \figref{fig:exampleFRF}.
Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
\begin{equation}
  \mathrm{SNR} 
    = \frac{\sigma_v}
           {\rms{\true{y}}}
    \approx \frac{\sigma_{v}}
                 {\left\| \true{G} \right\|_2 \rms{\true{u}}}
    =  \frac{\sigma_{v}}
            {\left\| \true{G} \right\|_2}
  \label{eq:SNR-definition}
  \text{.}
\end{equation}
is attained.
$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
